On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Beautify coordinates
Обновление картинок
[AMZAE] Add example of arrow-like set

\item
Figure~\ref{42_symm.png}:
\\
$\mathcal{P}_{42}=\sqrt{154}/{1} * \{
(\pm 345596160; 0);
(\pm219513840; -15069600);
(\pm260201760; 0);\\
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0);
(\pm25116000; 0);\\
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);\\
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);\\
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$

\item
Figure~\ref{46_symm.png}:
\\
$\mathcal{P}_{46}=\sqrt{154}/{1} * \{
(\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);\\
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);\\
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);\\
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);\\
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$

\item
Figure~\ref{48_symm.png}:
\\
$\mathcal{P}_{48}=\sqrt{154}/{1} * \{
( \pm10022288640; 0);
( \pm6365901360 ; -437018400);
( \pm7545851040 ; 0);\\
( \pm6547992360 ; 0);
( \pm6183810360 ; 0);
( \pm4464871320 ; 0);
( \pm4195376640 ; 0);
( \pm728364000 ; 0);\\
( \pm35860203808 ; 0);
( \pm34660241460 ; 0);
( \pm23985026520 ; 0);
( \pm20126778360 ; 0);\\
( \pm14926606240 ; 0);
( \pm13460166720 ; 0);
( \pm10414391260 ; 0);
( \pm2194803520 ; 0);
( \pm389293216 ; 0);\\
( \pm2672185425 ; 0);
( \pm9857846460 ; 0);
( \pm1293126240 ; 0);
( \pm17699891040 ; 0);
( \pm14408546880 ; 0);\\
( \pm3007524114 ; 0);
( \pm3402061572 ; 0)\}
$

@@

%\section{Arrow-like integral point sets with one axis of symmetry}

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline}
%
\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_d680ff2d172ebe40250a54ca9419af34_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

\begin{figure}[h!]
	\center{\includegraphics[width=1\linewidth]{./img/8_2400_42_56f33d8dc5df552595e807c438bc0f55_other.png}}
	\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2400}
	\label{8_2400_42_56f3}}
\end{figure}

>>>>

\item
Figure~\ref{42_symm.png}:
\begin{multline}
	\mathcal{P}_{42}=\sqrt{154}/{1} * \{
		(\pm219513840; -15069600);
		(\pm 345596160; 0);
		(\pm260201760; 0);
		\\
		(\pm225792840; 0);
		(\pm213234840; 0);
		(\pm153961080; 0);
		(\pm144668160; 0);
		(\pm25116000; 0);
		\\
		(\pm694026840; 0);
		(\pm514710560; 0);
		(\pm359116940; 0);
		(\pm13423904; 0);
		(\pm75682880; 0);
		\\
		(\pm464143680; 0);
		(\pm827069880; 0);
		(\pm92144325; 0);
		(\pm1195180740; 0);
		(\pm1236558752; 0);
		\\
		(\pm44590560; 0);
		(\pm339925740; 0);
		(\pm117312468; 0)
	\}
\end{multline}

\item
Figure~\ref{46_symm.png}:
\begin{multline}
	\mathcal{P}_{46}=
	\sqrt{154}/{1} * \{
		(\pm276778320; -19000800);
		(\pm435751680; 0);
		(\pm328080480; 0);
		\\
		(\pm268861320; 0);
		(\pm194124840; 0);
		(\pm182407680; 0);
		(\pm1559139296; 0);
		(\pm284695320; 0);
		\\
		(\pm1506967020; 0);
		(\pm1042827240; 0);
		(\pm875077320; 0);
		(\pm648982880; 0);
		(\pm585224640; 0);
		\\
		(\pm452799620; 0);
		(\pm95426240; 0);
		(\pm16925792; 0);
		(\pm116181975; 0);
		(\pm428602020; 0);
		\\
		(\pm56222880; 0);
		(\pm769560480; 0);
		(\pm626458560; 0);
		(\pm31668000; 0);
		(\pm130761918; 0)
	\}
\end{multline}

\item
Figure~\ref{48_symm.png}:
\begin{multline}
	\mathcal{P}_{48}=
	\sqrt{154}/{1} * \{
		( \pm6365901360 ; -437018400);
		( \pm10022288640; 0);
		( \pm23985026520 ; 0);
		\\
		( \pm389293216 ; 0);
		( \pm6183810360 ; 0);
		( \pm4464871320 ; 0);
		( \pm4195376640 ; 0);
		( \pm728364000 ; 0);
		\\
		( \pm35860203808 ; 0);
		( \pm34660241460 ; 0);
		( \pm7545851040 ; 0);
		( \pm20126778360 ; 0);
		\\
		( \pm14926606240 ; 0);
		( \pm13460166720 ; 0);
		( \pm10414391260 ; 0);
		( \pm2194803520 ; 0);
		\\
		( \pm2672185425 ; 0);
		( \pm9857846460 ; 0);
		( \pm1293126240 ; 0);
		( \pm17699891040 ; 0);
		\\
		( \pm14408546880 ; 0);
		( \pm3007524114 ; 0);
		( \pm6547992360 ; 0);
		( \pm3402061572 ; 0)
	\}
\end{multline}

@@

\section{Arrow-like integral point sets with one axis of symmetry}

Figure~\ref{17_1024296_1_639b}:
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/1*\{
		( -2847 ; \pm72072);
		( 47073 ; \pm124488);
		( 47073 ; 0);
		( \pm98943 ; 0);
		\\
		( -71487 ; 0);
		( -694668 ; 0);
		( 15457 ; 0);
		( 23582 ; 0);
		( 125307 ; 0);
		\\
		( 329628 ; 0);
		( -50367 ; 0);
		( -14943 ; 0);
		( 63073 ; 0);
		( 172207 ; 0)
	\}
\end{multline}

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/17_1024296_1_639b7a0452227fde1aceabf02e8778e4_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 17 and diameter 1024296}
\label{17_1024296_1_639b}}
\end{figure}

@@

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline}
%
\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

\begin{figure}[h!]
	\center{\includegraphics[width=1\linewidth]{./img/8_2400_42_symm.png}}
	\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2400}
	\label{8_2400_42_56f3}}
\end{figure}
